Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-03-12 apples_and_oranges.qmd
Attempts at tabulating

```{r, warning=FALSE, message = FALSE, echo=FALSE}
###########Libraries needed
library(tidyverse)
library(truncnorm)
library(metafor)
library(meta)
```

@@

@@

@@

### Number of sites
Write results, tabulate.

@@

df_sites_summary_stats <- df_baseline_demographics %>%
  group_by(psy_or_med) %>%
  summarise(
    mean_sites = mean(sites, na.rm = TRUE),
    sd_sites = sd(sites, na.rm = TRUE),
    n = n()
  )

@@

>>>>

```{r, warning=FALSE, message = FALSE, echo=FALSE}
###########Libraries needed
library(tidyverse)
library(truncnorm)
library(metafor)
library(meta)
library(kableExtra)
```

@@

# plot for overall severity results

@@

# Now lets make a table that combines across these baseline characteristics variables

df_overall_baseline_results <- rbind(results_met_perc_women_overall, results_met_age, results_met_sev)

# For row names
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(subgroup = case_when(
    row_number() == 1 ~ "Gender",
    row_number() == 4 ~ "Age",
    row_number() == 7 ~ "Severity",
    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
  ))

# Rounding
df_overall_baseline_results <- df_overall_baseline_results %>%
  mutate(across(where(is.numeric), ~round(., 2)))

df_overall_baseline_results %>%
  kbl(caption = "Sample characteristics at baseline") %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
  row_spec(row = 0, background = "#D3D3D3",  extra_css = "border-bottom: 2px solid grey;" ) %>% 
  row_spec(c(1, 4, 7), bold = T, extra_css = "border-top: 2px solid grey;") %>%
  column_spec(column = 1, border_right = T) %>% 
  add_indent(c(2, 3, 5, 6, 8, 9))

df_overall_baseline_results <- options(knitr.kable.NA = "")

```
### Number of trial sites

Average number of trial sites was significantly higher across medication studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 0]` compared to psychotherapy studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 1]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 1]`(*t* (`r sites_t_test$parameter`) = `r sites_t_test$statistic`, *p* = `r sites_t_test$p.value`).

@@

df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]

### Number of sites
# Write results, tabulate.

@@

# summary stats
df_sites_summary_stats <- df_baseline_demographics %>%
  group_by(psy_or_med) %>%
  summarise(
    n = n(),
    mean_sites = mean(sites, na.rm = TRUE),
    sd_sites = sd(sites, na.rm = TRUE),
  )

# t-test
sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)

@@

# Tabulate
# Rounding
df_sites_summary_stats <- df_sites_summary_stats %>%
  mutate(across(where(is.numeric), ~round(., 2)))

# Row names
df_sites_summary_stats <- df_sites_summary_stats %>%
  mutate(psy_or_med = case_when(
    psy_or_med == 0 ~ "Medication",
    psy_or_med == 1 ~ "Psychotherapy",
    TRUE ~ as.character(psy_or_med)  # Keep other values unchanged
  ))

df_sites_summary_stats %>%
  kbl(col.names = c("Modality", "N", "Mean", "SD")) %>% 
  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE)
